The paper on blockchain front-running

### 2018-09-22 frontrunning/Latex/sections/paper.tex
edits

Blockchain technology enables smart contracts or decentralized applications (DApps). Function calls (or transactions) to the DApp are processed by a decentralized network. Transactions are finalized in stages: they (generally) first relay around the network, then are selected by a miner and put into a valid block, and finally the block is well-enough incorporated that is unlikely to be reorganized. Front-running is an attack where a malicious node observes a transaction after it is broadcast but before it is finalized, and attempts to have its own transaction confirmed before or instead of the observed transaction. Whether this attack is beneficial depends on the logic of the DApp itself.

In this paper, we perform a number of case studies of DApps on Ethereum (a popular blockchain supporting DApps) that are volnerable to front-running attacks. We draw the cases from the top 25 most active DApps,\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} as well as ICOs which are absent from this list during a sampling period. xxx tend to appear on this list when they are actively issued.      benefit of this attack varies on what the DApps is doing but, this attack .

@@

As a preview, in Section~\ref{sec:frontrunningExchanges}), we examine Bancor~\cite{hertzog2017bancor}, a decentralized exchange that operates similar to traditional stock markets and is likewise volunerable to front-running. Domain name frontrunning occurs when a user uses a domain registrar to inquire if a domain is available for purchase, and the query triggers the registrar to purchase the domain in anticipation that it can sell it to the user. In Section~\ref{sec:ens}, we examine decentralized namespaces like Ethereum Name Service and academic works like Ghazal~\cite{moosavighazal} where relaying nodes and miners see Alice's attempt to purchase a domain name before it is finalized in a block. A front-running node might try to supersede her transaction. In Section~\ref{sec:ICOsfrontrunning}, we look at Initial Coin Offerings (ICOs). After a few hacking incidents of high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered. This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to latecomers on the open markets~\cite{zetzsche2018ico, li2018initial}. ICOs started to experiment with different fair capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}. We show empirical evidence of a miner purchasing tokens ahead of other users.

@@

Blockchain, as a secure ledger, gives the impression of an ultimate secure platform for decentral applications and one might not consider implementing the application with security in mind. In general, all the network participants have the ability to front-run specific transactions that are sent to the network. Also, miners can include any transactions they like into the block they attempt to mine. Thus, they possess special power in terms of front-running as opposed to other users of the network. In the following, we discuss and compare the two groups of blockchain potential front-runners.

\subsubsection{Blockchain Participants}
Any regular (miner or non-miner) the user can front-run other transactions in the network. For regular users to front-run others on the blockchain, they need to be well connected to other nodes on the network. Doing so, they are able to listen to the network and monitor all transactions that are broadcast. On the Ethereum blockchain, users have to pay for the computations in a small amount of Ether called \textit{gas}~\cite{AccountT67:online}. The price that users pay for transactions, \textit{gasPrice}, can increase or decrease how quickly miners will execute them and include them within the blocks they mine. Once seeing two identical transactions with different transaction fees, a rational miner will prioritize the transaction that pays a higher gas price per unit of gas --gasPrice--, this is due to limited space in the blocks while maximizes their profit in the block they mine. Therefore, any regular users who run a full-node Ethereum client can front-run pending transactions by sending similar transaction with higher gas price, see figure~\ref{fig:RegularFrontrunning}. For example, in a decentral exchange, he can monitor the network and once seeing a pending \textit{buy} transaction which will further increase the price of the asset, a front-runner can send a transaction with a higher gas price and hope to have his transaction mined ahead of the original pending transaction. By doing so, he achieves a better rate from the buyer. Note that in this case, blockchain front-runners are visible to the network as they broadcast their transactions to all the network participants. The probability of success in such attach can be increased by flooding the network by transactions with higher than average gasPrice.

@@

\subsubsection{Miners} \label{minersfrontrunning}
Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this in case of malicious reordering is known as \textbf{transaction reordering} attack. For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 units of a token\ie TKN, presumably if this transaction goes through, it causes the price of the purchased token to increase. So the dishonest miner can step in front of this transaction and place his own buy order ahead. He would simply create his \textit{buy} of 1000 TKN and include it in front of the previous \textit{buy} transaction in the block he mines. Doing so, he would receive a better rate than other network users, and afterward can sell the assets he has bought and gained a price advantage. It should be noted that miners can only front-run transactions within the blocks they happen to mine. They could do this also by not broadcasting their own transactions to the network before including it in the block, this makes the miners be less noticeable to the network when front-running.
Another example here is in the case of decentral exchanges and order cancellation. Every exchange should have the functionality to cancel the orders, especially for a volatile market. In this case, when the user decides that her order is not profitable anymore, she would send a cancelation transaction. Here the miner sees the cancelation transaction and puts his own transaction to fill that order in front of the cancellation transaction --transaction reordering--, potentially profiting from the order. He can also include the canceled transaction in the block to collect the full gas limit used by the cancel transaction~\cite{CostofDecentralization:online}, see figure~\ref{fig:MinerFrontrunning}. Front-running can also occur in non-financial smart contracts. As an example, a smart contract which adds all the participants to a party invite list could only be closed by the smart contract owner. In this case, when the owner sends the transaction to close the list, a miner can include his own list of participants before the close transaction in the block he mines. This is an issue with the design of the smart contracts and is known as transaction-ordering dependence vulnerability~\cite{luu2016making}.

>>>>

Blockchain technology enables smart contracts or decentralized applications (DApps). Function calls (or transactions) to the DApp are processed by a decentralized network. Transactions are finalized in stages: they (generally) first relay around the network, then are selected by a miner and put into a valid block, and finally the block is well-enough incorporated that is unlikely to be reorganized. Front-running is an attack where a malicious node observes a transaction after it is broadcast but before it is finalized, and attempts to have its own transaction confirmed before or instead of the observed transaction.

The mechanics of frontrunning works on all DApps but front-running is not beneficial on all DApps; it depends on its internal logic as well as any mitigations it might implement. This paper is a series of case studies of DApps deployed on Ethereum (a popular blockchain supporting DApps). We study DApps from each category of the top 25 most active\footnote{List of decentralized applications \url{https://DAppradar.com/DApps}} to assess their vulnerability to front-running attacks. We also study initial coin offerings (ICOs), which by happenstance, did not appear in the top 25 on our sample day. Proposals to eliminate or mitigate frontrunning from DApps are scattered across forums, proposed standards (called EIPs in Ethereum) and academic papers; we systemize them here.

@@

\textblue{[tk]} As a preview, in Section~\ref{sec:frontrunningExchanges}), we examine Bancor~\cite{hertzog2017bancor}, a decentralized exchange that operates similar to traditional stock markets and is likewise vulnerable to front-running. Domain name frontrunning occurs when a user uses a domain registrar to inquire if a domain is available for purchase, and the query triggers the registrar to purchase the domain in anticipation that it can sell it to the user. In Section~\ref{sec:ens}, we examine decentralized namespaces like Ethereum Name Service and academic works like Ghazal~\cite{moosavighazal} where relaying nodes and miners see Alice's attempt to purchase a domain name before it is finalized in a block. A front-running node might try to supersede her transaction. In Section~\ref{sec:ICOsfrontrunning}, we look at Initial Coin Offerings (ICOs). After a few hacking incidents of high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered. This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to latecomers on the open markets~\cite{zetzsche2018ico, li2018initial}. ICOs started to experiment with different fair capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}. We show empirical evidence of a miner purchasing tokens ahead of other users.

@@

%Blockchain, as a secure ledger, gives the impression of an ultimate secure platform for decentral applications and one might not consider implementing the application with security in mind. In general, all the network participants have the ability to front-run specific transactions that are sent to the network. Also, miners can include any transactions they like into the block they attempt to mine. Thus, they possess special power in terms of front-running as opposed to other users of the network. In the following, we discuss and compare the two groups of blockchain potential front-runners.

\paragraph{Full Nodes.}
Any regular (miner or non-miner) the user can front-run other transactions in the network. For regular users to front-run others on the blockchain, they need to be well connected to other nodes on the network. Doing so, they are able to listen to the network and monitor all transactions that are broadcast. On the Ethereum blockchain, users have to pay for the computations in a small amount of Ether called \textit{gas}~\cite{AccountT67:online}. The price that users pay for transactions, \textit{gasPrice}, can increase or decrease how quickly miners will execute them and include them within the blocks they mine. Once seeing two identical transactions with different transaction fees, a rational miner will prioritize the transaction that pays a higher gas price per unit of gas --gasPrice--, this is due to limited space in the blocks while maximizes their profit in the block they mine. Therefore, any regular users who run a full-node Ethereum client can front-run pending transactions by sending similar transaction with higher gas price, see figure~\ref{fig:RegularFrontrunning}. For example, in a decentral exchange, he can monitor the network and once seeing a pending \textit{buy} transaction which will further increase the price of the asset, a front-runner can send a transaction with a higher gas price and hope to have his transaction mined ahead of the original pending transaction. By doing so, he achieves a better rate from the buyer. Note that in this case, blockchain front-runners are visible to the network as they broadcast their transactions to all the network participants. The probability of success in such attach can be increased by flooding the network by transactions with higher than average gasPrice.

@@

\paragraph{Miners.} \label{minersfrontrunning}
Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this in case of malicious reordering is known as \textbf{transaction reordering} attack. For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 units of a token\ie TKN, presumably if this transaction goes through, it causes the price of the purchased token to increase. So the dishonest miner can step in front of this transaction and place his own buy order ahead. He would simply create his \textit{buy} of 1000 TKN and include it in front of the previous \textit{buy} transaction in the block he mines. Doing so, he would receive a better rate than other network users, and afterward can sell the assets he has bought and gained a price advantage. It should be noted that miners can only front-run transactions within the blocks they happen to mine. They could do this also by not broadcasting their own transactions to the network before including it in the block, this makes the miners be less noticeable to the network when front-running.
Another example here is in the case of decentral exchanges and order cancellation. Every exchange should have the functionality to cancel the orders, especially for a volatile market. In this case, when the user decides that her order is not profitable anymore, she would send a cancelation transaction. Here the miner sees the cancelation transaction and puts his own transaction to fill that order in front of the cancellation transaction --transaction reordering--, potentially profiting from the order. He can also include the canceled transaction in the block to collect the full gas limit used by the cancel transaction~\cite{CostofDecentralization:online}, see figure~\ref{fig:MinerFrontrunning}. Front-running can also occur in non-financial smart contracts. As an example, a smart contract which adds all the participants to a party invite list could only be closed by the smart contract owner. In this case, when the owner sends the transaction to close the list, a miner can include his own list of participants before the close transaction in the block he mines. This is an issue with the design of the smart contracts and is known as transaction-ordering dependence vulnerability~\cite{luu2016making}.
